### 2024-02-16 documentation/thesis/thesis_document.tex
.

As the following, the motivation for the development of this framework
is listed. The chapter provides a brief introduction into the problem
domain, delineates the scope and boundaries of the present research,
surveys the current state of the art in low-field \gls{mri} research and
applications, articulates the research question driving this thesis and
delineates the anticipated usecases and benefits that will be explored
and analysed throughout the study.

@@

To address this challenge, the thesis proposes the development of a
comprehensive hardware and software framework. The hardware system aims
to selectively measure magnetic fields at different locations or fully
around a permanent magnet using different sensors. Several existing
open-source software solutions implement individual parts, but do not
provide a complete data processing pipeline from acquisition to
analysis, and their data storage formats are not compatible with each
other.

The accompanying open-source software for this thesis is designed not
only to facilitate measurements with different sensors but also to
enable the characterisation of different objects.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Example_Hallbach_ring_with_cutouts_for_eight_magnets.png}
\caption{Example Hallbach ring with cutouts for eight magnets
\label{Example_Hallbach_ring_with_cutouts_for_eight_magnets.png}}
\end{figure}

@@

A Halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. The graphic
\ref{Example_Hallbach_ring_with_cutouts_for_eight_magnets.png} shows an
example \gls{cad} model of such a ring, in which in this case eight
cubic \emph{12x12x12mm} magnets are embedded to generate homogeneous
magnetic flux densities of around \emph{20mT}.

@@

The Halbach magnet incorporated in this system boasts a \emph{27cm}
diameter, a \emph{B0} field strength of \emph{50.4 mT}, and an
impressive homogeneity of \emph{2400}\gls{ppm} over a \emph{20cm}
diameter using smaller magnets (\emph{12 x 12 x 12 mm\^{}3}). This
exceptional homogeneity enables the utilization of coil-based gradients
for spatial encoding, significantly enhancing the flexibility of image
acquisition.

@@

\hypertarget{usecases}{%
\section{Usecases}\label{usecases}}

The following section defines possible usecases that the future project
need to cover. These usecases define the setup of the hard- and
software. These illustrate practical situations to understand the
functionality and added value of the implemented solution for the user.

The usecases are defined in the course of project planning and provide
an overview of how the user interacts with the project and what
functionalities can be expected. In the later accomplished evaluation
process \ref{usecase-evaluation}, the defined usecases are also used as
a reference to demonstrate the implemented capabilities of the solution.
This is essential for understanding the needs of the target group and
designing the end result accordingly.

@@

Chapter \ref{usecase-evaluation}. \textbf{Usecase Evaluation} describes
the application of the framework to the previously defined usecases and
thus forms the basis for later evaluation.

@@

Chapter \ref{conclusion-and-discussion}. \textbf{Conclusion and
Discussion} bringing together essential research components, it
synthesizes study outcomes, discusses implications, and provides
insights for future work. This section ensures closure and aids readers
in grasping the broader context and significance of the research.

@@

In addition, the low-cost sensor interface will serve as a development
platform for the data evaluation \gls{mrp} library and provide real
measurement data from magnets. In addition, the interface firmware
creates a basis for the development of a data protocol for exchanging
measured values.

This makes it easy to integrate an own measuring devices into the
\gls{mrp} ecosystem at a later date. This is only possible with a
minimal functional hardware and firmware setup and is developed for this
purpose first.

@@

The firmware is responsible for detecting the possible connected sensors
\ref{Implemented_digital_magnetic_field_sensors.csv} and query
measurements. This measured data can be forwarded to a host \gls{pc} via
a user interface and can then be further processed there.

An important component is that as many common sensors as possible can be
easily connected without having to adapt the firmware. This modularity
is implemented using abstract class design. These are initiated
according to the sensors found at startup. If new hardware is to be
integrated, only the required functions \ref{lst:CustomSensorClass} need
to be implemented.

@@

The flow chart
\ref{Unified_sensor_firmware_simplified_program_structure.png} shows the
start process and the subsequent main loop for processing the user
commands and sensor results. When the microcontroller is started, the
software checks whether known sensors are connected to \gls{i2c} or
\gls{uart} interfaces.

@@

The next initialisation system is dedicated for multi-sensor
synchronisation \ref{sensor-syncronisation-interface}. The last step in
the setup is to configure communication with the host or connected
\gls{pc}. All implemented microcontroller platforms used
(\emph{Raspberry Pi Pico}, \emph{STM32F4}) have a \gls{usb} slave port.

@@

Ring buffers are well suited for applications with variable data rates
and minimise the need for complex memory management. The buffer can be
read out by command and the result of the measurement is sent to the
host. Each sensor measurement result is transmitted from the buffer to
the host together with a time stamp and a sequential number. This
ensures that in a multi-sensor setup with several sensors. The
measurements are synchronized \ref{sensor-syncronisation-interface} in
time and are not out of sequence or drift.

@@

\begin{itemize}
\tightlist
\item
  Use with \gls{mrp} \ref{software-readout-framework}-library
\item
  Stand-alone mode via sending commands using built-in \gls{cli}
\end{itemize}

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly determine whether
the hardware is working properly after installation. The \gls{cli}
behaves like terminal programmes, displaying a detailed command
reference \ref{Sensors_(+cli).png} to the user after connecting. The
current measured value can be output using the \emph{readout} command
\ref{Query_sensors_b_value_using_(+cli).png}.

@@

The other option is to use the \gls{mrp}
\ref{software-readout-framework}-library. The serial interface is also
used here. However, after a connection attempt by the \gls{hal}
\ref{mrphal} module of the \gls{mrp}
\ref{software-readout-framework}-library, the system switches to binary
mode, which is initiated using the \emph{sbm} command. The same commands
are available as for \gls{cli}-based communication, but in a binary
format.

@@

One problem with the use of several sensors on one readout host \gls{pc}
is that the measurements may drift over time. On the one hand, \gls{usb}
latencies can occur. This can occur due to various factors, including
device drivers, data transfer speed and system resources. High-quality
\gls{usb} devices and modern drivers often minimise latencies.
Nevertheless, complex data processing tasks and overloaded \gls{usb}
ports can lead to delays.

@@

\begin{itemize}
\tightlist
\item
  \emph{Raspberry Pi OS Lite} - \gls{os} \emph{Debian bookworm x64},
\item
  \gls{mrp} \ref{software-readout-framework}-library - Version
  \emph{1.4.1}
\item
  Unified Sensor \ref{unified-sensor}-firmware - Version \emph{1.0.1}
\end{itemize}

@@

In order to enable the most stable possible synchronisation between
several sensors, an option has already been created to establish an
electrical connection between sensors. This is used together with the
firmware to synchronise the readout intervals. The schematic
\ref{Multi_sensor_synchronisation_wiring_example.png} shows how several
sensors must be wired together in order to implement this form of
synchronisation.

@@

Once the hardware has been prepared, the task of the firmware of the
various sensors is to find a common synchronisation clock. To do this,
the function \emph{register irq on sync pin} is overwritten. To set one
\emph{primary} and several \emph{secondary} sensors, each sensor waits
for an initial pulse on the SYNC-\gls{gpio}
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
Each sensor starts a random timer beforehand, which sends a pulse on the
sync line. All others receive this and switch to \emph{secondary} mode
and synchronise the measurements based on each sync pulse received.

@@

In single-sensor operation, this automatically jumps to \emph{primary}
sensor operation through the \emph{got impulse within 1000ms} branch
result. The synchronisation status can be queried via the user interface
\ref{communication-interface} using the \emph{opmode}
\ref{Query_opmode_using_(+cli).png} command. An important aspect of the
implementation here is that there is no numbering or sequence of the
individual sensors.

This means that for the subsequent readout of the measurements, it is
only important that they are taken at the same interval across all
sensors. The sensor differentiation takes place later in the \gls{mrp}
\ref{software-readout-framework}-library by using the sensor \gls{uuid}.

@@

Two functional sensor platforms
\ref{Build_sensors_with_different_capabilities.csv} are built in order
to create a solid test platform for later tests and for the development
of the \gls{mrp} \ref{software-readout-framework}-library with the
previously developed sensor concepts.

\begin{longtable}[]{@{}llll@{}}
\caption{Build sensors with different capabilities
\label{Build_sensors_with_different_capabilities.csv}}\tabularnewline
\toprule
& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
Fullsphere\ref{d-fullsphere}\tabularnewline
\midrule
\endfirsthead
\toprule
& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
Fullsphere\ref{d-fullsphere}\tabularnewline
\midrule
\endhead
Maximal magnet size & Cubic 30x30x30 & Cubic 30x30x30 & Cubic
20x20x20\tabularnewline
Sensor type & MMC5603NJ & TLV493D & TLV493D\tabularnewline
Sensor count & 1 & 2 & 1\tabularnewline
Scanmode & static (1 point) & static (2 points) & dynamic
(fullsphere)\tabularnewline
\bottomrule
\end{longtable}

These cover all the required functions described in the usecases
\ref{usecases}. The most important difference, apart from the sensor
used, is the \emph{scan mode}. In this context, this describes whether
the sensor can measure a \emph{static} fixed point on the magnet or if
the sensor can move \emph{dynamically} around the magnet using a
controllable manipulator.

@@

The 1D sensor
\ref{1D_sensor_construction_with_universal_magnet_mount.png} is the
simplest possible sensor that is compatible with the Unified Sensor
firmware \ref{firmware} platform.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
\caption{Full-Sphere sensor implementation using two Nema17 stepper
motors in a polar coordinate system
\label{Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}}
\end{figure}

The 3D full sphere sensor
\ref{Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
offers the possibility to create a 3D map of the inserted magnet.

The graphic
\ref{3D_plot_of_an_N45_12x12x12_magnet_using_the_3D_fullsphere_sensor.png}
shows the visualisation of such a scan in the form of a spherical 3D
map. On the sphere is the magnetic field strength, which is detected by
the sensor at the position. The transition from a fully positive field
strength (red) to a negative field strength (blue) is clearly
recognisable and corresponds to the orientation of the magnet in the
holder.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_3D_plot_of_an_N45_12x12x12_magnet_using_the_3D_fullsphere_sensor.png}
\caption{3D plot of an N45 12x12x12 magnet using the 3D fullsphere
sensor
\label{3D_plot_of_an_N45_12x12x12_magnet_using_the_3D_fullsphere_sensor.png}}
\end{figure}

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following section shows how existing hardware can be
integrated into the system. A temperature-compensated \emph{Voltcraft
GM-70} telsameter
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
used, which has a measuring range of \emph{0T} to \emph{3T} with a
resolution of \emph{0.1mT}. It offers an \emph{RS232} interface with a
documented protocol for connection to a \gls{pc}.

This connectivity makes it possible to make the device compatible with
the unified sensor ecosystem using a separate interface software
\cite{VoltcraftGM70Rest} executable on the host \gls{pc}. However,
it does not offer the range of functions that the unified sensor
firmware offers.

@@

The teslameter is connected to the microcontroller using two free
\gls{gpio}s in \gls{uart} mode. The firmware is adapted using a separate
build configuration. In order to be able to read and correctly interpret
the data from the microcontroller, the serial protocol of the sensor is
implemented in a customised version of the \emph{CustomSensor} class
\ref{lst:CustomSensorClass}.

@@

\begin{itemize}
\tightlist
\item
  Data acquisition - from hardware sensors \ref{unified-sensor} or other
  data sources
\item
  Storage - export of data in various open formats
  \ref{storage-and-datamanagement}
\item
  Analysis - algorithms to analyse different data sets \ref{analysis}
\end{itemize}

All these possible task parts is divided into different blocks and users
is given the possibility of adding their own functionalities.

As the following, this concept is referred to as \emph{user interaction
points} \ref{user-interaction-points} and is explained in the following
chapter.

@@

User interaction points represent the core concept of the developed
library and are intended to provide user-friendliness on the one hand
and the rapid development of own analysis and optimisation algorithms on
the other.

For this purpose, the library is divided into individual modules, which
are shown in the graphic
\ref{MRP_library_module_high_level_overview.png}. In combination, these
represent a typical measurement-analysis-evaluation workflow of data.
For this purpose, a module system with standardised functional patterns
and data types is developed and packed together in a extendable Python
library.

@@

According to this concept, the user should be able to replace individual
components from this chain with their own modules without having to
worry about implementing other of these to make the project work.

@@

A project called \emph{HalbachOptimisation}
\cite{HalbachOptimisation} implements a data analysis step and
optimizes a magnetic field that is as homogeneous as possible within a
circular section using given mechanical dimensions as input parameters
of the magnets used. For this purpose, a mutation of the magnet
positions and rotations is performed. The result is a list of positions
for each magnet.

The \emph{HalbachMRIDesigner} \cite{HalbachMRIDesigner} opensource
project, can generate basic \gls{cad} drawings for \gls{mri} magnets in
a Halbach configuration. To do this, the number of magnets and
additional parameters for the properties of the \gls{cad} model to be
created are passed to the function provided as input parameters using a
\gls{json} file. The result is an \emph{OpenSCAD} \cite{OpenSCAD}
based 3D model of the magnet holder.

@@

The library created is intended to solve one problem by providing
standardized and flexible data structures for use with this form of
magnetic field data. By separating the processing pipeline into defined
sub-steps, it should be possible to make individual modules and as a
result functionalities interchangeable by the user.

The implementation of the same functionalities looks as follows after
using the library:

@@

The last step is to call up the \emph{HalbachMRIDesigner}
\cite{HalbachMRIDesigner} project, which creates the \gls{cad} model
of the magnet holder. The data can also be exported as files here. To
make the project compatible, the function signatures are also adapted
here. In this case, more changes are required, as the configuration file
is loaded from the file system. This logic must be removed in order to
use the added meta data in the input parameter instead.

After these customisation steps, it is possible to execute both projects
one after the other and all required configuration parameters are
contained in the data structure looped through the individual steps as
meta data. This also maps the functionality of a project file, which can
be executed or passed on repeatedly.

@@

In each of these categories there are then several sub-categories
divided into User Interaction Points. An overview of these is given in
the subchapters as the following. There are also introductory examples
which provide an overview of the basic functions in the \emph{Examples}
\ref{examples} section, as well as further examples in the online
documentation \cite{MagneticReadoutProcessingReadTheDocs}.

@@

For this purpose, an open, documented export format must be selected.
Ideally, this should be human-readable and viewable with a simple text
editor. This eliminates all binary-based formats such as the Python
pickle built into Python.

@@

The following code snippet \ref{lst:json_export_format_example} shows
the \gls{json} structure which is generated when a measurement that
using the library is exported. It can be seen that by using the
\gls{json} format, all measurement points and metadata are available in
readable plain text.

@@

The exported example \ref{lst:json_export_format_example} contains the
following different object keys, which contain the following
information:

@@

\begin{itemize}
\tightlist
\item
  \emph{MRPReadingSourceStatic} - for 1D and 2D sensors such as
  \emph{1D: Single Sensor} \ref{d-single-sensor}
\item
  \emph{MRPReadingSourceFullsphere} - for 3D sensors such as \emph{3D:
  Fullsphere} \ref{d-fullsphere}
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \emph{MRPVisualization} - different table and graph based plots
\item
  \emph{MRPPolarVisualization} - fullsphere map plots
\end{itemize}

@@

In contrast to the \emph{MRPPolarVisualization} module, this provides
functions to create 2D map plots a polar coordinate system. This
requires measurement data with additionally set spatial coordinates.
These can be generated automatically with the \emph{3D: Fullsphere}
\ref{d-fullsphere} sensor, or the user must provide the spatial
information from another source.

@@

At the current described scenarios, it is only possible to detect and
use sensors that are directly connected to the host \gls{pc}. It has the
disadvantage that there must always be a physical connection. This can
make it difficult to install multiple sensors in measurement setups
where space or cable routing options are limited.

@@

When using sensors with different capabilites, these must be combined.
These are used to select the appropriate measurement mode for a
measurement. For this purpose, the \emph{info} command of each sensor is
queried. This information is added to the previously created \gls{lut}.
Duplicate entries are summarised (see Table
\ref{Sensor_capabilities_merging_algorithm.csv}) and returned to the
host when the \emph{info} \ref{lst:mtsc} command is received over
network.

\begin{lstlisting}[language=bash, caption={MRPproxy REST enpoiint query examples}, label=lst:mtsc]
# QUERY Network-Proxy capabilities
$ wget http://proxyinstance.local:5556/proxy/status
{"capabilities":[
"static",
"dynamic",
"axis_temp",
"axis_x"
]}
\end{lstlisting}

@@

The \emph{MRPReading} is the key module of the \gls{mrp} core. It is
used to manage the measurement data and can be imported and exported.
The following example \ref{lst:mrpexample_reading} shows how a
measurement is created and measurement points are added in the form of
\emph{MRPReadingEntry} instances.

@@

The example \ref{lst:mrpexample_simulation} illustrated the basic usage.
Different variations of the \emph{generate\_reading} function offers the
user additional parameterisation options, such as random polarisation
direction or a defined centre-of-gravity vector. The data is generated
in the background using the \emph{magpylib}
\cite{ortner2020magpylib} library according to the specified
parameters.

>>>>

As the following, the motivation for the development of this framework
is listed. The chapter provides a brief introduction into the problem
domain, delineates the scope and boundaries of the present research,
surveys the current state of the art in low-field \gls{mri} research and
applications, articulates the research question driving this thesis and
delineates the anticipated use cases and benefits that will be explored
and analysed throughout the study.

@@

To address this challenge, the thesis proposes the development of a
comprehensive hardware and software framework. The hardware system aims
to selectively measure magnetic fields at different locations or fully
around a permanent magnet using different sensors. Several existing
open-source software solutions implement individual parts, but do not
provide a complete data processing pipeline from acquisition to
analysis, and their data storage formats are not compatible with each
other. The accompanying open-source software for this thesis is designed
not only to facilitate measurements with different sensors but also to
enable the characterisation of different objects.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Example_Halbach_ring_with_cutouts_for_eight_magnets.png}
\caption{Example Halbach ring with cutouts for eight magnets
\label{Example_Halbach_ring_with_cutouts_for_eight_magnets.png}}
\end{figure}

@@

A Halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. The figure
\ref{Example_Halbach_ring_with_cutouts_for_eight_magnets.png} shows an
example \gls{cad} model of such a ring. In this generated model eight
cubic \emph{12x12x12mm} magnets are embedded to generate homogeneous
magnetic flux densities of around \emph{20mT}.

@@

The Halbach magnet incorporated in this system boasts a \emph{27cm}
diameter, a \emph{B0} field strength of \emph{50.4 mT}, and an
impressive homogeneity of \emph{2400}\gls{ppm} over a \emph{20cm}
diameter using smaller magnets (\(12 x 12 x 12 mm^3\)). This exceptional
homogeneity enables the utilization of coil-based gradients for spatial
encoding, significantly enhancing the flexibility of image acquisition.

@@

\hypertarget{use-cases}{%
\section{Use cases}\label{use-cases}}

The following chapter defines possible use cases that the future project
need to cover. These use cases define the setup of the hard- and
software. These illustrate practical situations to understand the
functionality and added value of the implemented solution for the user.

The use cases are defined in the course of project planning and provide
an overview of how the user interacts with the project and what
functionalities can be expected. In the later accomplished evaluation
process \ref{use-case-evaluation}, the defined use cases are also used
as a reference to demonstrate the implemented capabilities of the
solution. This is essential for understanding the needs of the target
group and designing the end result accordingly.

@@

Chapter \ref{use-case-evaluation}. \textbf{Use Case Evaluation}
describes the application of the framework to the previously defined use
cases and thus forms the basis for later evaluation.

@@

Chapter \ref{conclusion-and-discussion}. \textbf{Conclusion and
Discussion} bringing together essential research components, it
synthesizes study outcomes, discusses implications, and provides
insights for future work. This chapter ensures closure and aids readers
in grasping the broader context and significance of the research.

@@

In addition, the low-cost sensor interface will serve as a development
platform for the data evaluation \gls{mrp} library and provide real
measurement data from magnets. Further, the interface firmware creates a
basis for the development of a data protocol for exchanging measured
values.

It simplifies of own measuring devices into the \gls{mrp} ecosystem at a
later date. This is only applicable with a minimal functional hardware
and firmware setup; it is developed for this purpose in the first step.

@@

The firmware is responsible for detecting the possible connected sensors
from table \ref{Implemented_digital_magnetic_field_sensors.csv} and
query measurements. This measured data can be forwarded to a host
\gls{pc} via a user interface and can then be further processed there.

An important component is that as many common sensors as possible can be
easily connected without having to adapt the firmware. This modularity
is implemented using abstract class design. These are initiated
according to the sensors found at startup. If new hardware is to be
integrated, only the required functions from listing
\ref{lst:CustomSensorClass} need to be implemented.

@@

The figure
\ref{Unified_sensor_firmware_simplified_program_structure.png} shows a
flow chart of the start process after powering on the sensor and the
subsequent main loop for processing the user commands and sensor
results. When the microcontroller is started, the software checks
whether known sensors are connected to \gls{i2c} or \gls{uart}
interfaces.

@@

The next initialisation system is dedicated for multi-sensor
synchronisation described in chapter
\ref{sensor-syncronisation-interface}. The last step in the setup is to
configure communication with the host or connected \gls{pc}. All
implemented microcontroller platforms used (\emph{Raspberry Pi Pico},
\emph{STM32F4}) have a \gls{usb} slave port.

@@

Ring buffers are well suited for applications with variable data rates
and minimise the need for complex memory management. The buffer can be
read out by command and the result of the measurement is sent to the
host. Each sensor measurement result is transmitted from the buffer to
the host together with a time stamp and a sequential number. This
ensures that in a multi-sensor setup with several sensors. The
measurements are synchronized in time and are not out of sequence or
drift.

@@

\begin{itemize}
\tightlist
\item
  Use with \gls{mrp}-library - see chapter
  \ref{software-readout-framework}
\item
  Stand-alone mode via sending commands using built-in \gls{cli}
\end{itemize}

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly determine whether
the hardware is working properly after installation. The \gls{cli}
behaves like terminal programmes, displaying a detailed command
reference as shown in the figure \ref{Sensors_(+cli).png} to the user
after connecting. The figure
\ref{Query_sensors_b_value_using_(+cli).png} shows the current measured
value queried by using the \emph{readout} command by the user.

@@

The other option is to use the devloped \gls{mrp}-library from chapter
\ref{software-readout-framework}. The serial interface is also used
here. However, After a connection attempt by the \gls{hal} \ref{mrphal}
module of the \gls{mrp}-library \ref{software-readout-framework} , the
system switches to binary mode, which is initiated using the \emph{sbm}
command. The same commands are available as for \gls{cli}-based
communication, but in a binary format.

@@

One problem with the use of several sensors on one readout host \gls{pc}
is that the measurements may drift over time. On the one hand, \gls{usb}
latencies can occur. This can occur due to various factors, including
device drivers, data transfer speed and system resources. High-quality
\gls{usb} devices and modern drivers often minimise
latencies.\cite{Wimmer2019} Nevertheless, complex data processing
tasks and overloaded \gls{usb} ports can lead to delays.

@@

\begin{itemize}
\tightlist
\item
  \emph{Raspberry Pi OS Lite} - \gls{os} \emph{Debian bookworm x64},
\item
  \gls{mrp}-library (see chapter \ref{software-readout-framework}) -
  Version \emph{1.4.1}
\item
  Unified Sensor-firmware - Version \emph{1.0.1}
\end{itemize}

@@

In order to enable the most stable possible synchronisation between
several sensors, an option has already been created to establish an
electrical connection between sensors. This is used together with the
firmware to synchronise the readout intervals. The figure
\ref{Multi_sensor_synchronisation_wiring_example.png} illustrates the
schematic how several sensors must be wired together in order to
implement this form of synchronisation.

@@

Once the hardware has been prepared, the task of the firmware of the
various sensors is to find a common synchronisation clock. To do this,
the function \emph{register irq on sync pin} is overwritten. To set one
\emph{primary} and several \emph{secondary} sensors, each sensor waits
for an initial pulse on the SYNC-\gls{gpio}. A random timer is started
beforehand by each sensor, which sends a pulse on the sync line. All
others receive this and switch to \emph{secondary mode} and synchronise
the measurements based on each sync pulse received.

@@

In single-sensor operation, this automatically jumps to \emph{primary}
sensor operation through the \emph{got impulse within 1000ms} branch
result. The figure \ref{Query_opmode_using_(+cli).png} shows the
synchronisation status of the sensor which can be queried via the user
interface described in chapter \ref{communication-interface} by using
the \emph{opmode} command. An important aspect of the implementation
here is that there is no numbering or sequence of the individual
sensors.

This means that for the subsequent readout of the measurements, it is
only important that they are taken at the same interval across all
sensors. The sensor differentiation takes place later in the
\gls{mrp}-library \ref{software-readout-framework} by using the sensor
\gls{uuid}.

@@

Two functional sensor platforms are built in order to create a solid
test platform for later tests and for the development of the
\gls{mrp}-library \ref{software-readout-framework} with the previously
developed sensor concepts.

\begin{longtable}[]{@{}llll@{}}
\caption{Build sensors with different capabilities
\label{Build_sensors_with_different_capabilities.csv}}\tabularnewline
\toprule
& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
Fullsphere\ref{d-fullsphere}\tabularnewline
\midrule
\endfirsthead
\toprule
& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
Fullsphere\ref{d-fullsphere}\tabularnewline
\midrule
\endhead
Maximal magnet size & Cubic 30x30x30mm & Cubic 30x30x30mm & Cubic
20x20x20mm\tabularnewline
Sensor type & MMC5603NJ & TLV493D & TLV493D\tabularnewline
Sensor count & 1 & 2 & 1\tabularnewline
Scanmode & static (1 point) & static (2 points) & dynamic
(fullsphere)\tabularnewline
\bottomrule
\end{longtable}

The table \ref{Build_sensors_with_different_capabilities.csv} shows the
various prototype sensor platforms equipped with different magnetic
field sensors. These cover all the required functions described in the
use cases \ref{use-cases}. The most important difference, apart from the
sensor used, is the \emph{scan mode}. In this context, this describes
whether the sensor can measure a \emph{static} fixed point on the magnet
or if the sensor can move \emph{dynamically} around the magnet using a
controllable manipulator.

@@

The 1D sensor shown in figure
\ref{1D_sensor_construction_with_universal_magnet_mount.png} is the
simplest possible sensor that is compatible with the Unified Sensor
firmware \ref{firmware} platform.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Full-sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
\caption{Full-sphere sensor implementation using two Nema17 stepper
motors in a polar coordinate system
\label{Full-sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}}
\end{figure}

The 3D full sphere sensor shown in figure
\ref{Full-sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
offers the possibility to create a 3D map of the inserted magnet.

The figure
\ref{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_3D_full-sphere_sensor.png}
shows the visualisation of such a scan in the form of a spherical 3D
map. On the sphere is the magnetic field strength, which is detected by
the sensor at the position. The transition from a fully positive field
strength (red) to a negative field strength (blue) is clearly
recognisable and corresponds to the orientation of the magnet in the
holder.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_3D_plot_of_an_N45_12x12x12mm_magnet_using_the_3D_full-sphere_sensor.png}
\caption{3D plot of an N45 12x12x12mm magnet using the 3D full-sphere
sensor
\label{3D_plot_of_an_N45_12x12x12mm_magnet_using_the_3D_full-sphere_sensor.png}}
\end{figure}

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following chapter shows how existing hardware can be
integrated into the system. A temperature-compensated \emph{Voltcraft
GM-70} telsameter shown in figure
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
used, which has a measuring range of \emph{0T} to \emph{3T} with a
resolution of \emph{0.1mT}. It offers an \emph{RS232} interface with a
documented protocol for connection to a \gls{pc}.

This connectivity makes it possible to make the device compatible with
the unified sensor ecosystem using a separate
\href{https://github.com/RBEGamer/VoltcraftGM70Rest}{interface software}
executable on the host \gls{pc}. However, it does not offer the range of
functions that the unified sensor firmware offers.

@@

The teslameter is connected to the microcontroller using two free
\gls{gpio}s in \gls{uart} mode. The firmware is adapted using a separate
build configuration. In order to be able to read and correctly interpret
the data from the microcontroller, the serial protocol of the sensor is
implemented in a customised version of the \emph{CustomSensor} class as
shown in listing \ref{lst:CustomSensorClass}.

@@

\begin{itemize}
\tightlist
\item
  Data acquisition - from hardware sensors or other data sources - see
  chapter \ref{unified-sensor}
\item
  Storage - export of data in various open formats - see chapter
  \ref{storage-and-datamanagement}
\item
  Analysis - algorithms to analyse different data sets - see chapter
  \ref{analysis}
\end{itemize}

All these steps are divided into different blocks with an editional
functionality for users to add own modules. This concept is explained in
the following chapter.

@@

User interaction points represent one core concept of the developed
library and are intended to provide user-friendliness on the one hand
and the rapid development of own analysis and optimisation algorithms on
the other. For this thesis it also eases the option to change sensors
for measurments.

For this purpose, the library is divided into individual modules, which
are shown in the figure
\ref{MRP_library_module_high_level_overview.png}. In combination, these
represent a typical measurement-analysis-evaluation workflow of data.
For this purpose, a module system with standardised functional patterns
and data types is developed and packed together in a extendable Python
library.

@@

According to this concept, the user should be able to replace individual
components from this chain with own modules without having to worry
about implementing other of these to make the project work.

@@

A project called \emph{HalbachOptimisation}
\cite{HalbachOptimisation} implements a data analysis step and
optimizes a magnetic field that is as homogeneous as possible within a
circular section using given mechanical dimensions as input parameters
of the magnets which are used. For this purpose, a mutation of the
magnet positions and rotations is performed. The result is a list of
positions for each magnet.

The \emph{HalbachMRIDesigner} \cite{HalbachMRIDesigner} is an
opensource project and generates basic \gls{cad} drawings for \gls{mri}
magnets in a Halbach configuration. To do this, the number of magnets
and additional parameters for the properties of the \gls{cad} model to
be created are passed to the function provided as input parameters using
a \gls{json} file. The result is an \emph{OpenSCAD} \cite{OpenSCAD}
based 3D model of the magnet holder.

@@

The library created is intended to solve this compatibility problem by
providing standardized and flexible data structures with this format of
magnetic field data. By separating the processing pipeline into defined
sub-steps, it is feasible to connect individual modules and as a result
functionalities interchangeable by the user.

The implementation of the same functionalities appears as the following
by using the library:

@@

The last step is to call up the \emph{HalbachMRIDesigner}
\cite{HalbachMRIDesigner} project, which creates the \gls{cad} model
of the magnet holder. The data can also be exported as files. To make
the project compatible, the function signatures are also adapted. In
this case, more changes are required, as the configuration file is
loaded from the file system. This logic needs to be removed in order to
use the added meta data as input parameter instead.

After these customisation steps, executing both projects one after the
other is possible and all required configuration parameters are
contained in the data structure looped through the individual steps as
meta data. This also maps the functionality of a project file, which can
be executed or passed on repeatedly.

@@

In each of these categories there are then several sub-categories
divided into User Interaction Points. An overview of these is given in
the subchapters as the following. There are also introductory examples
which provide an overview of the basic functions in the \emph{Examples}
\ref{examples} chapter, as well as further examples in the
\href{https://magneticreadoutprocessing.readthedocs.io/en/latest/}{online documentation}.

@@

For this purpose, an open, documented export format must be selected.
Ideally, this should be human-readable and viewable with a simple text
editor. This eliminates all binary-based formats such as the
\href{https://docs.python.org/3/library/pickle.html}{Python-Pickle}
package.

@@

The following listing \ref{lst:json_export_format_example} shows an
example \gls{json} structure which is generated when a measurement that
using the library is dumped to the filesystem. It can be seen that by
using the \gls{json} format, all measurement points and metadata are
available in readable plain text.

@@

The exported example listing \ref{lst:json_export_format_example}
contains different object keys, which contain the following information:

@@

\begin{itemize}
\tightlist
\item
  \emph{MRPReadingSourceStatic} - for 1D and 2D sensors such as
  \emph{1D: Single Sensor} \ref{d-single-sensor}
\item
  \emph{MRPReadingSourceFullSphere} - for 3D sensors such as \emph{3D:
  Full Sphere} \ref{d-full-sphere}
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \emph{MRPVisualization} - different table and graph based plots
\item
  \emph{MRPPolarVisualization} - full sphere map plots
\end{itemize}

@@

In contrast to the \emph{MRPPolarVisualization} module, this provides
functions to create 2D map plots a polar coordinate system. This
requires measurement data with additionally set spatial coordinates.
These can be generated automatically with the \emph{3D: Full Sphere}
\ref{d-full-sphere} sensor, or the user must provide the spatial
information from another source.

@@

In the previouse described scenarios, it is only possible to detect and
use sensors that are directly connected to the host \gls{pc}. It has the
disadvantage that there must always be a physical connection. This can
make it difficult to install multiple sensors in measurement setups
where space or cable routing options are limited.

@@

When using sensors with different capabilites, these must be combined.
These are used to select the appropriate measurement mode for a
measurement. For this purpose, the \emph{info} command of each sensor is
queried. This information is added to the previously created \gls{lut}.
Duplicate entries are summarised (see table
\ref{Sensor_capabilities_merging_algorithm.csv}) and returned to the
host when the \emph{info} \ref{lst:mtsc} command is received over
network.

\begin{lstlisting}[language=bash, caption={MRPproxy REST entrypoint query examples}, label=lst:mtsc]
# QUERY Network-Proxy capabilities
$ wget http://proxyinstance.local:5556/proxy/status
{"capabilities":[
"static",
"dynamic",
"axis_temp",
"axis_x"
]}
\end{lstlisting}

@@

The \emph{MRPReading} is the key module of the \gls{mrp} core. It is
used to manage the measurement data and can be imported and exported.
The following example listing \ref{lst:mrpexample_reading} shows how a
measurement is created and measurement points are added in the form of
\emph{MRPReadingEntry} instances.

@@

The example listing \ref{lst:mrpexample_simulation} illustrated the
basic usage. Different variations of the \emph{generate\_reading}
function offers the user additional parameterisation options, such as
random polarisation direction or a defined centre-of-gravity vector. The
data is generated in the background using the \emph{magpylib}
\cite{ortner2020magpylib} library according to the specified
parameters.
